Higher-Order unification for free!

### 2024-05-03 paper/main.tex
corrected example of mapdedup

\paragraph{Example of \mapdeduplication}
If we take back the example give at the beginning of this section,
\mapdeduplication produces the following result:
% 
% make test ONLY=7007 TEX=tex
\printAlll
  {{{\lambda x.(X\appsep x),a},
    {X,\lambda x.a}}}
  {{{A,a},
    {C,\lambda x.a}}}
  {{{X,B,1}}}
  {{{\eta,,C,\lambda x.B_{x}},
    {\eta,,A,\lambda x.B_{x}}}}

\noindent
Note that $\mapping{X}{C}{0}$ desappears from \mapStore
\todo{update this description to match the example} 
in favour of the auxiliary \linketa \linketaM{x}{E_{x}}{\lambda y.C_{x y}}.
The resolution of $\hoUnifPb_1$ assignes $a$ to $A$. This wakes up
$\linkStore_2$ by \progressetaleft, assigning <<$a \appsep x$>> to $B_x$.
The resolution of $\hoUnifPb_2$ instantiates $C$ to $\lambda x.a$, which, in
turn triggers $\linkStore_1$ by \progressetaleft. This link perfroms
$\lambda x.a \Ue \lambda x.(a \appsep x)$, which, as expected, fails.

>>>>

\paragraph{Example of \mapdeduplication}
If we take back the example given at the beginning of this section,
\mapdeduplication produces the following result:
% 
% make test ONLY=7007 TEX=tex
\printAlll
  {{{\lambda x.(X\appsep x),a},
    {X,\lambda x.a}}}
  {{{A,a},
    {C,\lambda x.a}}}
  {{{X,B,1}}}
  {{{\eta,,C,\lambda x.B_{x}},
    {\eta,,A,\lambda x.B_{x}}}}

\noindent
Note that $\mapping{X}{C}{0}$ desappears from \mapStore
in favour of the auxiliary \linketa \linketaM{}{C}{\lambda x.B_{x}}.
The resolution of $\hoUnifPb_1$ assignes $a$ to $A$. This wakes up
$\linkStore_2$ by \progressetaleft, assigning <<$a \appsep x$>> to $B_x$.
The resolution of $\hoUnifPb_2$ instantiates $C$ to $\lambda x.a$, which, in
turn triggers $\linkStore_1$ by \progressetaleft. This link perfroms
$\lambda x.a \Ue \lambda x.(a \appsep x)$, which, as expected, fails.
